Modelling last glacial cycle ice dynamics in the Alps

### 2017-11-14 articles/cycle/alps-cycle.tex
Add lo-res compute time and Younger Dryas timing.
Add references to Hantke and German maps.

    These simulations use a horizontal resolution of 2\,km. The vertical grid
    consists of 31~temperature layers in the bedrock and up to 126~enthalpy
    layers in the ice, corresponding to vertical resolutions of 100 and
    40\,m, respectively. Simulations ran for \todo{how long?}
    using 36~processors.

@@

    For the three palaeo-temperature records and the two palaeo-precipitation
    parametrizations used, the model yields significant ice volume build-up
    during MIS~4 and 2 (Fig.~\ref{fig:timeseries}b), corresponding to documented
    glaciation periods in the Alps \citep{Preusser.2004, Ivy-Ochs.etal.2008}.
    All simulations also yield important glaciations during MIS~5 and 3, but
    their timing and amplitude varies significantly depending on the climate
    forcing used. All six simulations overestimate the late-glacial re-advance
    during the Younger Dryas
    \citep[\todo{timing}, cf. e.g.,][]{Ivy-Ochs.etal.2009}.
    This is partly because the 2\,km resolution used in these simulations is
    too coarse to resolve
    Younger Dryas Alpine glaciers. However, the large total ice volume
    overestimation resulting from the GRIP temperature forcing
    (Fig.~\ref{fig:timeseries}b, blue curves) certainly indicates that the
    vigorous cooling experienced in Greenland is not representative of the
    Alps.

@@

    The LGM extent of Alpine glaciers has been mapped with varying level of
    detail across the Western \citep{Coutterand.2010,
    Buoncristiani.Campy.2011}, Central \citep{Jackli.1962, Bini.etal.2009}
    \todo{ref. Hantke}, and Eastern Alps \citep{Penck.Bruckner.1909,
    Husen.1987, Husen.2011, Bavec.Verbic.2011} \todo{ref. German Geologische
    Übersichtskarte 1:200,000}. Some of these maps have been compiled
    into a reconstruction, covering the entire Alps \citep{Ehlers.etal.2011},
    and reproduced here (Fig.~\ref{fig:lgmvel}, red line) for comparison
    against model results.

>>>>

    These simulations use a horizontal resolution of 2\,km. The vertical grid
    consists of 31~temperature layers in the bedrock and up to 126~enthalpy
    layers in the ice, corresponding to vertical resolutions of 100 and
    40\,m, respectively. Simulations ran for two to four days
    using 144~processors.

@@

    For the three palaeo-temperature records and the two palaeo-precipitation
    parametrizations used, the model yields significant ice volume build-up
    during MIS~4 and 2 (Fig.~\ref{fig:timeseries}b), corresponding to documented
    glaciation periods in the Alps \citep{Preusser.2004, Ivy-Ochs.etal.2008}.
    All simulations also yield important glaciations during MIS~5 and 3, but
    their timing and amplitude varies significantly depending on the climate
    forcing used. All six simulations overestimate the late-glacial re-advance
    during the Younger Dryas
    \citep[12.9--11.7\,ka; cf. e.g.,][]{Ivy-Ochs.etal.2009}.
    This is partly because the 2\,km resolution used in these simulations is
    too coarse to resolve
    Younger Dryas Alpine glaciers. However, the large total ice volume
    overestimation resulting from the GRIP temperature forcing
    (Fig.~\ref{fig:timeseries}b, blue curves) certainly indicates that the
    vigorous cooling experienced in Greenland is not representative of the
    Alps.

@@

    The LGM extent of Alpine glaciers has been mapped with varying level of
    detail across the Western \citep{Coutterand.2010,
    Buoncristiani.Campy.2011}, Central \citep{Jackli.1962, Bini.etal.2009,
    Hantke.2011}, and Eastern Alps \citep{Penck.Bruckner.1909, Husen.1987,
    BGR.2007, Husen.2011, Bavec.Verbic.2011}.
    Some of these maps have been compiled
    into a reconstruction, covering the entire Alps \citep{Ehlers.etal.2011},
    and reproduced here (Fig.~\ref{fig:lgmvel}, red line) for comparison
    against model results.
